---
title: "Data Analytics Assignment #3"
author: "Scout Oatman-Gaitan"
date: "2/19/2020"
output: pdf_document
---

## Q1. Choose any 5 of the nyt datasets except nyt1, perform the following:

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
nyt10 <- read.csv("nyt10.csv")
nyt11 <- read.csv("nyt11.csv")
nyt12 <- read.csv("nyt12.csv")
nyt13 <- read.csv("nyt13.csv")
nyt14 <- read.csv("nyt14.csv")
```


#### a). Create boxplots for all 5 datasets for each of two key variables (you choose the variables), i.e. two figures (one for each variable) with 5 boxplots (for the 5 different datasets) in each. Describe/summarize the distributions. min. 3-4 sentences (3%)
```{r}
boxplot(nyt10$Impressions, nyt11$Impressions, 
        nyt12$Impressions, nyt13$Impressions, 
        nyt14$Impressions, na.rm = T)
```
Impressions Distribution: Each of the 5 datasets have positively skewed distributions. Q1 (~3), Median (~5), and Q3 (~6) are all very similar across the five sets and they all have outliers outside of the upper outlier range.
```{r}
boxplot(nyt10$Clicks, nyt11$Clicks, nyt12$Clicks, 
        nyt13$Clicks, nyt14$Clicks, na.rm = T)
```
Clicks Distribution: This distribution is unique. Lower outlier range = Q1 = Median = Q3 = Upper outlier range = 0. This makes it so that any value not equal to 0 is a positive outlier. This tells us that in general, the articles do not get clicks and getting even 1 click is a statistical outlier. 


#### b). Create histograms for all 5 datasets for two key variables – can be the same variables in 1a or different (you choose the histogram bin width). Describe the distributions in terms of known parametric distributions and similarities/ differences among them. min. 3-4 sentences (3%)
```{r}
#code
```

#### c). Plot the ECDFs (Empirical Cumulative Distribution Function for your two key variables. Plot the quantile-quantile distribution using a suitable parametric distribution you chose in 1b. Describe features of these plots. min. 3-4 sentences (4000-level 5%, 6000-level 3%)
```{r}
#code
```

#### d). Perform a significance test that is suitable for the variables you are investigating. Discuss the test results and indicate whether the null hypothesis is valid. min. 3-4 sentences (4000-level 4%, 6000-level 3%) 
```{r}
#code
```

#### e). Discuss any observations you had about the datasets/ variables, other data in the dataset (0% ;-))

```{r}
#code
```

## Q2. 6600-level question (3%). Filter the distributions you explored in Q1 using one or more of the other variables for only 2 (not 5) of the nyt datasets. Repeat Q1b, Q1c and Q1d and draw any conclusions from this study. min. 3-4 sentences
```{r}
#code
```

