---
title: "US Consumer Finance Complaints"
date: "October 11, 2016"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width='900px', dpi=200)
library(plyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(plotly)
library(RColorBrewer)
library(choroplethrMaps)
library(choroplethr)
library(tm)
library(wordcloud)
library(RColorBrewer)
```

Each week the CFPB sends thousands of consumers’ complaints about financial products and services to companies for response. Those complaints are published here after the company responds or after 15 days, whichever comes first. By adding their voice, consumers help improve the financial marketplace.

Click <http://www.consumerfinance.gov/data-research/consumer-complaints/> for more information on the dataset.


```{r echo=FALSE, warning=FALSE}
complaints <- read.csv("complaints.csv")
```

## Sneak peak into the dataset


```{r echo=FALSE}
dim(complaints)

str(complaints)

names(complaints)
```

## Univariate Analysis

### Products

* What are the different products?
* How many complaints raised against each product?


```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

#table(complaints$Product)

ggplot(complaints, aes(reorder(Product, -table(complaints$Product)[Product]), fill = Product)) + geom_bar() + xlab("Product") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 80, size = 5, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none")

```

### Companies
 
* How many different companies?
* What are the top 10 and bottom 10 companies based on the number of complaints?

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

by_company <- complaints %>% group_by(Company) %>% select(Company) %>% summarise(Count = n()) %>% arrange(desc(Count))

#head(by_company, 10)
#tail(by_company, 10)

ggplot(head(by_company, 7), aes(reorder(Company, -Count), Count, fill = Company)) + geom_bar(stat = "identity") + xlab("Sub Product") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 15, size = 9, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none")

```

Biggest banks have thousands of complaints while the ones at the bottom are smaller ones which is obvious.

### State


* How is the distribution of the complaints across the country?

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

by_state <- complaints %>% group_by(State) %>% select(State) %>% summarise(Count = n()) %>% arrange(desc(Count))

head(by_state, 10)
tail(by_state, 10)

ggplot(head(by_state, 10), aes(reorder(State, -Count), Count, fill = State)) + geom_bar(stat = "identity") + xlab("State") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none" )

```

There are more than 50 states in the State column. These include even the federal as well as inhabited territories.
Also the states with most complaints look like the ones which are highly populated states of the country.

### Timely response

* How many complaints have received timely response?

```{r echo=FALSE}

table(complaints$Timely.response.)

prop.table(table(complaints$Timely.response.))

```

Almost 97.5% of the complaints have been addressed timely.
Given the competition in the financial sector and also the challenges posed by the FINTECH start-ups established players have to do lot more to resolve the complaints. 


### Consumer disputed

* How many consumer disputed?


```{r echo=FALSE}

table(complaints$Consumer.disputed.)

prop.table(table(complaints$Consumer.disputed.))

```

Over 20% of the users disputed.


### Submitted Via

* How are these complaints submitted?


```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

table(complaints$Submitted.via)

prop.table(table(complaints$Submitted.via))


ggplot(complaints, aes(reorder(Submitted.via, -table(complaints$Submitted.via)[Submitted.via]), fill = Submitted.via)) + geom_bar() + xlab("Mode of Complaints Submission") + ylab("Number of Complaints") + scale_y_continuous(breaks = seq(0,1200000,100000)) + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none")

```

Majority of the complaints are filed through the web and least method used is email.

### Company Response

* What are the different responses users get from the companies?


```{r echo=FALSE}

table(complaints$Company.response.to.consumer)

prop.table(table(complaints$Company.response.to.consumer))

```

Majority are closed with explanation and around 20% are closed with some relief.


### Time taken to send the complaint to company

* Creating new variable

```{r echo=FALSE}

complaints$Date.received <- as.Date(complaints$Date.received, "%Y-%m-%d")

complaints$Date.sent.to.company <- as.Date(complaints$Date.sent.to.company, "%Y-%m-%d")

complaints$Days_to_send_to_company <- difftime(complaints$Date.sent.to.company, complaints$Date.received , units = c("days"))

complaints$Days_to_send_to_company <- as.numeric(complaints$Days_to_send_to_company)

summary(complaints$Days_to_send_to_company)

dim(complaints[complaints$Days_to_send_to_company > 100, ])
comp100 <- subset(complaints, Days_to_send_to_company >100)

dim(complaints[complaints$Days_to_send_to_company > 500, ])
comp500 <- subset(complaints, Days_to_send_to_company >500)

dim(complaints[complaints$Days_to_send_to_company > 900, ])
comp900 <- subset(complaints, Days_to_send_to_company >900)

```

* Very surprising that it took more than 100 days for 3K complaints to be sent to companies.
* There are also some data entry issues where the days took is in negative. Date received is after the date sent which is a data entry issue.
* One complaint took 900 days to be sent to company.
```{r}
View(comp100)
View(comp900)
```


### Create new variable month and year

* Extract month and year from the date complaint received.
* Distribution of the complaints across different months and years

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

complaints$Month <- month(ymd(complaints$Date.received))

complaints$Year <- year(ymd(complaints$Date.received))

complaints$Month <- factor(complaints$Month)
complaints$Year <- factor(complaints$Year)

table(complaints$Month)
table(complaints$Year)

```
```{r}
ggplot(complaints, aes(Month, fill = Month)) + geom_bar() + theme(plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none")

ggplot(complaints, aes(Year, fill = Year)) + geom_bar() + scale_y_continuous(breaks = seq(0,350000,50000)) + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none")
```


* First three months of the year have the most complaints.
* Complaints are increasing over the years
* 2015 being the worst year
* Will be interesting to see how many end up in 2016.

# Bivariate Analysis

### Products against other variables

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

table(complaints$Product, complaints$Submitted.via)

ggplot(complaints, aes(reorder(Product, table(complaints$Product)[Product]), fill = Submitted.via )) + geom_bar() + xlab("Product") + ylab("Number of Complaints") + coord_flip() + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15))

table(complaints$Product, complaints$Timely.response.)

ggplot(complaints, aes(reorder(Product, table(complaints$Product)[Product]), fill =  Timely.response. )) + geom_bar() + xlab("Product") + ylab("Number of Complaints") + coord_flip() + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15))


table(complaints$Product, complaints$Company.response.to.consumer)

ggplot(complaints, aes(reorder(Product, table(complaints$Product)[Product]), fill = Company.response.to.consumer )) + geom_bar() + xlab("Product") + ylab("Number of Complaints")  + coord_flip()

table(complaints$Product, complaints$Year)

ggplot(complaints, aes(reorder(Product, table(complaints$Product)[Product]), fill = Year )) + geom_bar() + xlab("Product") + ylab("Number of Complaints")  + coord_flip()

```


### Year against other variables


```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

table(complaints$Year, complaints$Submitted.via)

ggplot(complaints, aes(Year, fill = Submitted.via )) + geom_bar(position = "dodge") + xlab("Year") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) 

table(complaints$Year, complaints$Timely.response.)

ggplot(complaints, aes(Year, fill = Timely.response. )) + geom_bar(position = "dodge") + xlab("Year") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) 

table(complaints$Year, complaints$Company.response.to.consumer)

ggplot(complaints, aes(Year, fill = Company.response.to.consumer )) + geom_bar() + xlab("Year") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none")

table(complaints$Year, complaints$Consumer.disputed.)

ggplot(complaints, aes(Year, fill = Consumer.disputed. )) + geom_bar(position = "dodge") + xlab("Year") + ylab("Number of Complaints") + scale_y_continuous(breaks = seq(0,350000,50000)) + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) 

```

* Year on Year there is increase in number of people raising complaints through the web which seems to be acceptable given the developments in the digital banking
* All the open complaints were raised in 2016 accept 1 which was in 2015


### States against other variables

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

ggplot(complaints, aes(reorder(State, table(complaints$State)[State]),fill = Submitted.via )) + geom_bar() + xlab("States") + ylab("Number of Complaints") + coord_flip()

ggplot(complaints, aes(reorder(State, table(complaints$State)[State]), fill = Company.response.to.consumer )) + geom_bar() + xlab("States") + ylab("Number of Complaints") + coord_flip()

ggplot(complaints, aes(reorder(State, table(complaints$State)[State]), fill = Consumer.disputed. )) + geom_bar() + xlab("States") + ylab("Number of Complaints") + coord_flip()

```

* There are certain records which do not have any value for state.
* There are also records which do not belong to the 50 states
* Not many resolutions disputed.
* Most populated states are having more complaints raised.


### Top 10 States


```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

top10_states <- complaints %>% group_by(State) %>% summarise(Total = n()) %>% arrange(desc(Total)) %>% head(10)

top10_states$State <- factor(top10_states$State)

ggplot(top10_states, aes(reorder(State, -Total), Total, fill = State)) + geom_bar(stat = "identity")  + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) + theme(legend.position = "none") + xlab("State")

top10_states_data <- subset(complaints, State %in% top10_states$State)

top10_states_data$State <- factor(top10_states_data$State)

table(top10_states_data$State, top10_states_data$Consumer.disputed.)

ggplot(top10_states_data, aes(reorder(State, -table(top10_states_data$State)[State]), fill = Consumer.disputed. )) + geom_bar() + xlab("States with most Complaints") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15))

table(top10_states_data$State, top10_states_data$Submitted.via)

ggplot(top10_states_data, aes(reorder(State, -table(top10_states_data$State)[State]), fill = Submitted.via )) + geom_bar() + xlab("States with most Complaints") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15)) 

table(top10_states_data$State, top10_states_data$Company.response.to.consumer)

ggplot(top10_states_data, aes(reorder(State, -table(top10_states_data$State)[State]), fill = Company.response.to.consumer )) + geom_bar() + xlab("States with most Complaints") + ylab("Number of Complaints") + theme(axis.text.x = element_text(angle = 50, size = 10, vjust = 0.4, face = "bold"), plot.title = element_text(size = 20, face = "bold", vjust = 2),axis.title.x = element_text(face = "bold", size = 15, vjust = -0.35),axis.title.y = element_text(face = "bold", vjust = 0.35, size = 15))

```



### Companies


```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

length(unique(complaints$Company))

top10_companies <- complaints %>% group_by(Company) %>% summarise(Total = n()) %>% arrange(desc(Total)) %>% head(10)

top10_companies$Company <- factor(top10_companies$Company)

top10_companies$Company

top10_companies <- subset(complaints, Company %in% top10_companies$Company)
dim(top10_companies)[1]/dim(complaints)[1]


ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Product)) + geom_bar() + coord_flip() + ggtitle("Companies with most complaints against products") + ylab("Number of Complaints") + xlab("Companies")

ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Consumer.disputed. )) + geom_bar() + coord_flip() + ggtitle("Companies with most complaints against Consumer_disputed") + ylab("Number of Complaints") + xlab("Companies") 


ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Consumer.disputed. )) + geom_bar(position = "dodge") + ggtitle("Companies with most complaints against Consumer_disputed") + ylab("Number of Complaints") + xlab("Companies") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) 

ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Company.response.to.consumer )) + geom_bar() + coord_flip() + ggtitle("Companies with most complaints against Company_response_to_consumer") + ylab("Number of Complaints") + xlab("Companies")

```

* More than 50% of the complaints are raised against the products of the top 10 companies.
* Three of the top 10 are dealing only with credit reporting products. These are well known credit reporting firms.
* Student loan complaints are very few among the top 10
* Precard complaints are very minimal which is very acceptable as most of the people use credit cards these days.


# Mapping Complaints 

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

data("state.regions")

tomap <- complaints %>% group_by(State) %>% summarise(Total = n()) 
tomap <- subset(tomap, State %in% state.abb)
tomap <- as.data.frame(tomap)
names(tomap) <- c("region", "value")

tomap$region <- state.regions[match(tomap$region, state.regions$abb), 1]

## Map1
#state_choropleth(tomap, title = "Complaints by State", legend = "Number of Complaints")

## Map2
state_choropleth(num_colors = 9, tomap, title = "Complaints by State", legend = "Number of Complaints")

# Map3 by company
mapdata <- complaints[complaints$State !="",] %>% group_by(State, Company) %>% summarise(Total = n()) %>% arrange(desc(Total))
mapdata$company <- factor(mapdata$Company)
tomap_3 <- by(mapdata, mapdata["State"], head, n=1)
tomap_3 <- Reduce(rbind, tomap_3)

tomap_3$Company <- factor(tomap_3$Company)
tomap_3 <- tomap_3[,-3]
tomap_3 <- subset(tomap_3, State %in% state.abb)
names(tomap_3) <- c("region", "value")

tomap_3$region <- state.regions[match(tomap_3$region, state.regions$abb), 1]
tomap_3$value <- factor(tomap_3$value)
table(tomap_3$value)


choro = StateChoropleth$new(tomap_3)
choro$title = "Financial Consumer Complaints - Companies with Most Complaints Statewise"
choro$ggplot_scale = scale_fill_manual(name="Company", values=c("red", "orange", "lightblue", "yellow", "blue"), drop=FALSE)
#choro$ggplot_scale = scale_fill_manual(name="Company", values=c("#a6cee3", "#e31a1c", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#fdbf6f", "#ff7f00", "#cab2d6", "#6a3d9a"), drop=FALSE)
#choro$render()


# Map4 by product
mapdata <- complaints[complaints$State !="",] %>% group_by(State, Product) %>% summarise(Total = n()) %>% arrange(desc(Total))
mapdata$Product <- factor(mapdata$Product)
tomap_4 <- by(mapdata, mapdata["State"], head, n=1)
tomap_4 <- Reduce(rbind, tomap_4)

tomap_4$Product <- factor(tomap_4$Product)
tomap_4 <- tomap_4[,-3]
tomap_4 <- subset(tomap_4, State %in% state.abb)
names(tomap_4) <- c("region", "value")

tomap_4$region <- state.regions[match(tomap_4$region, state.regions$abb), 1]
tomap_4$value <- factor(tomap_4$value)
table(tomap_4$value)


choro = StateChoropleth$new(tomap_4)
choro$title = "Products with Most Complaints Statewise"
choro$ggplot_scale = scale_fill_manual(name="Products", values=c("lightblue", "red", "blue"), drop=FALSE)
#choro$ggplot_scale = scale_fill_manual(name="Company", values=c("#a6cee3", "#e31a1c", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#fdbf6f", "#ff7f00", "#cab2d6", "#6a3d9a"), drop=FALSE)
choro$render()



# Map5 by Year
mapdata <- complaints[complaints$state !="",] %>% group_by(state, Year) %>% summarise(Total = n()) %>% arrange(desc(Total))
mapdata$Year <- factor(mapdata$Year)
tomap_5 <- by(mapdata, mapdata["state"], head, n=1)
tomap_5 <- Reduce(rbind, tomap_5)
head(tomap_5)
tomap_5$Year <- factor(tomap_5$Year)
tomap_5 <- tomap_5[,-3]
tomap_5 <- subset(tomap_5, state %in% state.abb)
names(tomap_5) <- c("region", "value")

tomap_5$region <- state.regions[match(tomap_5$region, state.regions$abb), 1]
tomap_5$value <- factor(tomap_5$value)
table(tomap_5$value)


choro = StateChoropleth$new(tomap_5)
choro$title = "Year with Most Complaints Statewise"
choro$ggplot_scale = scale_fill_manual(name="Products", values=c( "red", "blue"), drop=FALSE)
choro$render()
```

* More the populations more the users of the financial products which in turn resulting in more complaints.
* 30 states have most complaints against BOA
* Wells Fargo comes second
* 43 States have most complaints against Mortage
* 41 States had most complaints in 2015 and 9 in 2014

# Multvariate Analysis

### Products and other variables

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

ggplot(complaints, aes(reorder(Product, -table(complaints$Product)[Product]), fill = Submitted.via )) + geom_bar() + xlab("Product") + ylab("Number of COmplaints") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + facet_wrap(~Year)

ggplot(complaints, aes(reorder(Product, -table(complaints$Product)[Product]), fill = Submitted.via )) + geom_bar() + xlab("Product") + ylab("Number of COmplaints") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + facet_wrap(~Month)

ggplot(complaints, aes(reorder(Product, -table(complaints$Product)[Product]), fill = Submitted.via )) + geom_bar() + xlab("Product") + ylab("Number of COmplaints") + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) + facet_wrap(~company_response_to_consumer)

```


### Companies and other variables

```{r echo=FALSE, warning=FALSE, fig.width=9, fig.height=5.5}

#ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Submitted.via)) + geom_bar() + ggtitle("Companies with most complaints") + ylab("Number of Complaints") + xlab("Companies") + facet_wrap(~Year) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Product)) + geom_bar() +  ggtitle("Companies with most complaints") + ylab("Number of Complaints") + xlab("Companies") + facet_wrap(~Year) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

#ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Company.response.to.consumer)) + geom_bar() + ggtitle("Companies with most complaints") + ylab("Number of Complaints") + xlab("Companies") + facet_wrap(~Year) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
 
#ggplot(top10_companies, aes(reorder(Company, table(top10_companies$Company)[Company]), fill = Company.response.to.consumer)) + geom_bar() +  ggtitle("Companies with most complaints") + ylab("Number of Complaints") + xlab("Companies") + facet_wrap(~Month) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))

```


* Spike in the number of credit reporting complaints from 2012 to 2015
* Top 3 banks have been able to pull down the number of complaints related to financial products from 2012 to 2015
* Number of complaints filed through referrals has gone down for the top 3 banks.
* Complaints closed without relief are mostly during the first half of the year


